Generalising Weighted Model Counting to Boolean Algebras

### 2020-04-11 paper.tex
A bit of progress

\section{Implications for Lifted Inference}

\subsection{Preliminaries}

@@

\begin{definition}[\cite{givant2008introduction}]
  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
  $\mathbf{A}$ with a family of inclusion maps $\{ \iota_i\colon \mathbf{A}_i
  \to \mathbf{A} \}_{i \in I}$. If for any BA $\mathbf{B}$ with a family of
  homomorphisms $\{ f_i\colon \mathbf{A} \to \mathbf{B} \}_{i \in I}$ there
  exists a unique common extension of $\{ f_i\colon \mathbf{A} \to \mathbf{B}
  \}_{i \in I}$ ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
  \[
    \begin{tikzcd}
      \mathbf{A}_i \arrow{r}{\iota_i} \arrow{rd}[swap]{f_i} & \mathbf{A} \arrow[d,dashed,"f"] \\
      & \mathbf{B}
    \end{tikzcd}
  \]
  then $\mathbf{A}$ is the \emph{internal sum}\footnote{A slightly more general
    version of this definition is also known as the free product, the Boolean
    product, and the coproduct in the category of BAs
    \cite{givant2008introduction,koppelberg1989handbook,sikorski1969boolean}.}
  of $\{\mathbf{A}_i \}_{i \in I}$. We will denote it as $\bigoplus_{i \in I}
  \mathbf{A}_i$.
\end{definition}

\begin{proposition}[\cite{sikorski1969boolean}]
  Let $\mathbf{A}$ be the internal sum of a family of BAs $\{ \mathbf{A}_i \}_{i
    \in I}$, and let $\{m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in
    I}$ be a family of measures. Then there exists a unique measure $m\colon
  \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any finite subset $J
  \subseteq I$ and family of elements $\{ x_j \in \mathbf{A}_j \}_{j \in J}$,
  \[
    m \left( \bigwedge_{j \in J} x_j \right) = \prod_{j \in J} m_j(x_j).
  \]
\end{proposition}
% TODO: this suggest a new rule for lifted inference.

\subsection{New Results}

\bibliographystyle{plain}
\bibliography{paper}

>>>>

\section{Representing Independence and Conditional Independence}

\subsection{Independence (all known results)}

@@

\begin{definition}[\cite{givant2008introduction}]
  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of subalgebras of a BA
  $\mathbf{A}$. If for any BA $\mathbf{B}$ with a family of homomorphisms $\{
  f_i\colon \mathbf{A}_i \to \mathbf{B} \}_{i \in I}$ there exists a unique
  common extension of $\{ f_i\colon \mathbf{A}_i \to \mathbf{B} \}_{i \in I}$
  ($f\colon \mathbf{A} \to \mathbf{B}$ in the diagram),
  \[
    \begin{tikzcd}
      \mathbf{A}_i \ar[r,hookrightarrow] \arrow{rd}[swap]{f_i} & \mathbf{A}
      \arrow[d,dashed,"f"] \\
      & \mathbf{B}
    \end{tikzcd}
  \]
  then $\mathbf{A}$ is the \emph{internal sum}\footnote{A slightly more general
    version of this definition is also known as the free product, the Boolean
    product, and the coproduct in the category of BAs
    \cite{givant2008introduction,koppelberg1989handbook,sikorski1969boolean}.}
  of $\{\mathbf{A}_i \}_{i \in I}$. We will denote it as $\bigoplus_{i \in I}
  \mathbf{A}_i$.
\end{definition}

\begin{proposition}[\cite{sikorski1969boolean}]
  Let $\mathbf{A}$ be the internal sum of a family of BAs $\{ \mathbf{A}_i \}_{i
    \in I}$, and let $\{m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in
    I}$ be a family of measures. Then there exists a unique measure $m\colon
  \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any finite subset $J
  \subseteq I$ and family of elements $\{ x_j \in \mathbf{A}_j \}_{j \in J}$,
  \[
    m \left( \bigwedge_{j \in J} x_j \right) = \prod_{j \in J} m_j(x_j).
  \]
\end{proposition}

\subsection{Conditional Independence}

\begin{definition}[\cite{koppelberg1989handbook}]
  Let $\mathbf{A}$ be a BA. Let $\mathbf{B}$ be a subalgebra of $\mathbf{A}$,
  and let $(\mathbf{A}_i)_{i \in I}$ be a family of subalgebras of $\mathbf{A}$
  such that $\mathbf{A}_i \cap \mathbf{A}_j = \mathbf{B}$ for all $i \ne j$ in
  $I$. Let $\{ \iota_i \colon \mathbf{B} \to \mathbf{A}_i \}$ be a family of
  inclusion homomorphisms. Then $\mathbf{A}$ is the \emph{amalgamated free
    product\footnote{Also known as a (wide) pushout in the category of BAs.} of
    $\{\mathbf{A}_{i} \}_{i \in I}$ over $\mathbf{B}$} if, for any Boolean
  algebra $\mathbf{C}$ with a family of homomorphisms $\{ f_i\colon \mathbf{A}_i
  \to \mathbf{C} \}_{i \in I}$ such that $f_i \circ \iota_i = f_j \circ \iota_j$
  for all $i, j \in I$, there is a unique homomorphism $f\colon \mathbf{A} \to
  \mathbf{C}$ such that the triangle in
  \[
    \begin{tikzcd}
      \mathbf{B} \ar[r,hookrightarrow,"\iota_i"] & \mathbf{A}_i
      \ar[r,hookrightarrow] \ar[d,swap,"f_i"] & \mathbf{A} \ar[ld,dashed,"f"] \\
      & \mathbf{C}
    \end{tikzcd}
  \]
  commutes for all $i \in I$. We will denote this product as
  \[
    \mathbf{A} = \bigoplus_{\substack{\mathbf{B}\\ i \in I}} \mathbf{A}_i.
  \]
\end{definition}

\subsubsection{New Results}

\begin{theorem}
  Let $\{ \mathbf{A}_i \}_{i \in I}$ be a family of BAs with measures $\{
  m_i\colon \mathbf{A}_i \to \mathbb{R}_{\ge 0} \}_{i \in I}$, let $\mathbf{B}$
  be a BA, and let $\mathbf{A}$ be the amalgamated free product of $\{
  \mathbf{A}_i \}_{i \in I}$ over $\mathbf{B}$. Then there is a unique measure
  $m\colon \mathbf{A} \to \mathbb{R}_{\ge 0}$ such that, for any element $b \in
  \mathbf{B}$, finite subset $J \subseteq I$, and elements $\{ a_j \in
  \mathbf{A}_j \}_{j \in J}$,
  \[
    m \left(b \land \bigwedge_{j \in J} a_j \right) = \prod_{j \in J} m_j(b
    \land a_j).
  \]
\end{theorem}

\bibliographystyle{plain}
\bibliography{paper}
% TODO: curly brackets or parentheses for families? Maybe curly brackets
